---
title: "Example Workflow"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is an Example Workflow for J5 Opentrons Usage

### Parse the Combinatorial File

```{r J5_data_parsing}
#directory for parse_j5 already defined in setup
parse_j5(path = "./J5_EricZirkle_GH3_mCherry/")
```

### Dilute Oligos

Dilutions Tasks-
Ask what is being diluted(Which Primer) (Pop up that matches oWL ID in spreadsheet)
-Check if there is any in stock that is already diluted from OWL or another spreadsheet (Grab
information from spreadsheet)
-If no stock (If else statement/loop)
-Confirm what is being diluted (reconfirm the oWL ID)
-Calculate appropriate dilution volume to dilute 10x to 10uM (perform 10x dilution into

appropriate tube)
-Else If stock available
-Check date
-If less than one month old, use primer (display message: “Primer in stock and

fresh” and kick out)

-If greater than one month old, assume no stock assumption and redilute (go

back and assume no stock and perform no stock loop)

Pseudo code:
Take information from the parsing code
Compare primers in the file to the oWL spreadsheet (for stock)

If (primer name stock not available):
pipette.pick_up_tip(tiprack[&#39;A1&#39;])
pipette.aspirate((amount needed for dilution), plate[&#39;NFW&#39;], rate=2.0)
pipette.dispense(Amount from aspiration, plate[&#39;Primer&#39;], rate=2.0)
pipette.blow_out()
Else (primer available)
Compare Date
If date &lt; 30 days
Perform operation
Else date &gt;30 days
No stock option



